---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# HYPEtools

<!-- badges: start -->
[![R-CMD-check](https://github.com/rcapell/HYPEtools/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/rcapell/HYPEtools/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

This repository contains source files for an R package HYPEtools, which provides functions to work with files from and for the hydrological model HYPE. 

## Summary
HYPEtools is an add-on package to the [R software environment](http://www.r-project.org/), providing functions to work with the hydrological model [HYPE](http://hype.sourceforge.net/). HYPE and HYPEtools are projects developed by the [Swedish Meteorological and Hydrological Institute (SMHI)](http://www.smhi.se/en).

## Installation

You can install the development version of HYPEtools from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rcapell/HYPEtools")
```

[Here you can read how to install the provided sources or package in R.](Install-and-Update-HYPEtools-from-github)

## Vignettes

Browse HYPEtools Vignettes like so:

```{r example}
library(HYPEtools)
browseVignettes("HYPEtools")
```

